Sensors Lab Conference

### 2020-12-11 Paper/Paper.tex
Minor fixes to paper tex

The Time-Slotted Channel Hopping (TSCH) mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the Internet of Things (IoT). Its ﬂexibility makes the TSCH mode a very promising candidate for the future of the MAC layer in LLNs. As such, its performance under different conditions must be assessed, so that accurate guidelines for its application can be drawn\cite{TSCHExperimentEval}.
\begin{figure}[]
	\centering
	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
	\label{fig:6tischStack}
\end{figure}

@@

\begin{itemize}
\item MAKE_MAC=MAKE_MAC_TSCH
\item MAKE_NET=MAKE_NET_NULLNET
\item MAKE_ROUTING=MAKE_ROUTING_NULLROUTING
\end{itemize}

MAKE_MAC_TSCH tells the Make system to build the TSCH MAC layer, MAKE_NET_NULLNET essentially disables the network layer, MAKE_ROUTING_NULLROUTING does the same for routing functionality.

@@

\label{section:preprocessdef}
\begin{itemize}
\item $ENERGEST_CONF_ON=1$: Enable the energest package to allow analysis of power use. 
\item $TSCH_SCHEDULE_CONF_WITH_6TISCH_MINIMAL=0$: Disable creation of a default TSCH schedule. Instead we create our own, as described in section \ref{section:tschschedule}.
\item $LLSEC802154_CONF_ENABLED=0$: Disable Link Layer security.
\item $TSCH_CONF_JOIN_SECURED_ONLY=0$: Allow TSCH to join unsecured networks.
\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK_MAC.on() function), rather than starting it immediately when the node powers on.
\end{itemize}

@@

With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly 9.6 \frac{mJ}{kbit} for the leaf and 11.5 \frac{mJ}{kbit} for the root.

@@

%\begin{figure}[]
%	\centering
%	\includegraphics[width=.5\textwidth,keepaspectratio]{1m_powerStates.png}
%	\caption{The time a node spends in each power state at 1 meter seperation.}
%	\label{fig:powerState1m}
%\end{figure}
%\begin{figure}[]
%	\centering
%	\includegraphics[width=.5\textwidth,keepaspectratio]{5m_powerStates.png}
%	\caption{The time a node spends in each power state at 5 meters seperation.}
%	\label{fig:powerState5m}
%\end{figure}

%PACKET ARRIVAL RATE: 1.0
%AVERAGE LATENCY: 9.291666666666666
%LEAF ENERGY CONSUMPTION: 4.347331036560059 J
%ROOT ENERGY CONSUMPTION: 2.577431278930664 J
%Since each packet carried a data payload of 52 bytes, that's
%	LEAF: 10.701122551532452 J/kbit
%	ROOT: 6.344446225060096 J/kbit
%PACKET ARRIVAL RATE: 1.0
%AVERAGE LATENCY: 9.333333333333334
%LEAF ENERGY CONSUMPTION: 4.345094247253417 J
%ROOT ENERGY CONSUMPTION: 2.578182406585693 J
%Since each packet carried a data payload of 52 bytes, that's
%	LEAF: 10.695616608623796 J/kbit
%	ROOT: 6.346295154672475 J/kbit

>>>>

The Time-Slotted Channel Hopping (TSCH) mode for medium access control (MAC) included in the standard IEEE 802.15.4 has been designed as the multichannel MAC protocol for Low-power and lossy networks (LLNs), a key component of the Internet of Things (IoT). Its ﬂexibility makes the TSCH mode a very promising candidate for the future of the MAC layer in LLNs. As such, its performance under different conditions must be assessed, so that accurate guidelines for its application can be drawn\cite{TSCHExperimentEval}.
\begin{figure}[]
	\centering
	\includegraphics[width=.25\textwidth,keepaspectratio]{6TiSCH-Protocol-Stack.png}
	\caption{6TiSCH Protocol Stack\cite{TimeCritical6tisch}.}
	\label{fig:6tischStack}
\end{figure}}

@@

\begin{itemize}
\item MAKE\_MAC=MAKE\_MAC\_TSCH
\item MAKE\_NET=MAKE\_NET\_NULLNET
\item MAKE\_ROUTING=MAKE\_ROUTING\_NULLROUTING
\end{itemize}

MAKE\_MAC\_TSCH tells the Make system to build the TSCH MAC layer, MAKE\_NET\_NULLNET essentially disables the network layer, MAKE\_ROUTING\_NULLROUTING does the same for routing functionality.

@@

\label{section:preprocessdef}
\begin{itemize}
\item $ENERGEST_CONF_ON=1$: Enable the energest package to allow analysis of power use. 
\item $TSCH_SCHEDULE_CONF_WITH_6TISCH_MINIMAL=0$: Disable creation of a default TSCH schedule. Instead we create our own, as described in section \ref{section:tschschedule}.
\item $LLSEC802154_CONF_ENABLED=0$: Disable Link Layer security.
\item $TSCH_CONF_JOIN_SECURED_ONLY=0$: Allow TSCH to join unsecured networks.
\item $TSCH_CONF_AUTOSTART=0$: Allow the program to start TSCH manually (using the NETSTACK\_MAC.on() function), rather than starting it immediately when the node powers on.
\end{itemize}

@@

With a total data size of 360 kilobits (12 tests * 60 packets * 64 bytes per packet * 8 bits per byte / 1024 bits per kilobit), that corresponds to roughly $9.6 \frac{mJ}{kbit}$ for the leaf and $11.5 \frac{mJ}{kbit}$ for the root.

@@
